Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-14 journal paper/content/sim_details.tex
Revised a footnote re BEG.

\xhdr{MAB algorithms.} We consider the three classes of bandit algorithms discussed in Section~\ref{sec:intro-model}, and look for qualitative differences between them. We take a representative algorithm from each class. Our pilot experiments indicate that our findings do not change substantially if other representative algorithms are chosen. 
We use Thompson Sampling (\TS) from the ``adaptive-exploration" MAB algorithms, Bayesian Epsilon-Greeedy (\DEG) with exploration probability $\eps=5\%$ from the ``exploration-separating" algorithms,%
\footnote{Our pilot experiments show that different $\eps$ did not qualitatively change the results.}  and \DynGreedy algorithm (\DG) as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.
Self-contained background can be found in Appendix~\ref{sec:related-classes}.

>>>>

\xhdr{MAB algorithms.} We consider the three classes of bandit algorithms discussed in Section~\ref{sec:intro-model}, and look for qualitative differences between them. We take a representative algorithm from each class. Our pilot experiments indicate that our findings do not change substantially if other representative algorithms are chosen. 
We use Thompson Sampling (\TS) from the ``adaptive-exploration" algorithms, Bayesian Epsilon-Greeedy (\DEG) with exploration probability $\eps=5\%$ from the ``exploration-separating" algorithms,%
\footnote{In each round, \DEG algorithm explores uniformly with a predetermined probability $\eps$, and ``exploits" with the remaining probability, choosing an arm with maximal posterior mean reward given the current data. Our pilot experiments show that choosing a different exploration probability $\eps$ does not qualitatively change the results.}  and \DynGreedy (\DG) algorithm  as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.
Self-contained background can be found in Appendix~\ref{sec:related-classes}.
